Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data

### 2020-02-22 article.tex
some conclutions added to experiments and results

>>>>

Test results suggest that the algorithm can classify Parkinson's patients precisely while avoiding overfitting. The approach of investigating time-slices separately has made our model faster and gave us the ability to distinguish patients from healthy controls more accurately. In addition to that, the proposed method was able to give a prediction about Parkinson's disease by a single time-slice while being $93.77\%$ correct. Moreover, the combination of all time-slices together enabled us to improve accuracy to $97.92\%$. Other criterias such as Sensitivity, Specificity, Positive and negative predictive values are acceptably high and the only wrong prediction can be seen in Test 3 (Table \ref{table:tests_3}).
